Future challenges for Research Software Engineering

### 2025-05-19 future_challenges_for_RSEng.tex
Proof-reading edits by GC (#37)
* Fix order of authors

* Language edits

* Add missing space

* Minor language edits in ethics

% society implications
The work being undertaken by RSEs may well have direct, or indirect,
ethical implications in areas such as social engineering \cite{s2erc,siadati2024},
climate \cite{Lannelongue2023} and more.
Another example might be that they are developing code that can also be used for military purposes, such as numerical solvers or computer vision systems.
As engineers, RSEs take the responsibility for the software they develop.
RSEs need to be aware of these issues and develop their own ``red lines''.
With the advantages of \autoref{sec:ai} in place, ever-more AI created artifacts will be in the world.
Therefore we expect a discussion within societies about their acceptable use to take place.

>>>>

% society implications
The work being undertaken by RSEs may well have direct, or indirect,
ethical implications in areas such as social engineering \cite{s2erc,siadati2024},
climate \cite{Lannelongue2023} and more.
Another example might be that they are developing code that can also be used for military purposes, such as numerical solvers or computer vision systems.
As engineers, RSEs take the responsibility for the software they develop.
RSEs need to be aware of these issues and develop their own ``red lines''.
With the advantages of \autoref{sec:ai}, ever-more AI created artifacts will be included in research.
As a result of this, we expect a discussion within societies about their acceptable use.
